A pipeline to analyse time-course gene expression data

### 2019-08-15 scripts/manuscript.Rmd
FIX install_github (which ain't called anymore
Update TODO list
ENH now contrasts can be provided as vector of strings

- Add legends to the plots that don't have.
- Make clear that it applies to RNASeq and how to call the different functions
    to RNASeq
- Check that clustering can deal with count data.

```{r eval=FALSE}
library(devtools)
install_github("NelleV/moanin", dependencies)

@@

We start by creating the `splines_model` object using the
`create_splines_model` function. The `splines_model` object contains a number
of metadata and options used throughout this analysis: the condition and
timepoints of each samples, the formula object used or the basis or the
degrees of freedom of the model. The metadata data.frame object should
contain at least two columns: one named `Group`, containing the  treatement
effect, and a second one named `Timepoint` containing the timepoint
information.

@@

If no formula is provided, it will default to the following: 
`formula = ~Group:ns(Timepoint, df=degrees_of_fredoom) + Group + 0`

Here we have provided the meta data that defines... `create_splines_model`
will .... **FIXME add information about what meta data is expected, describe
what `create_splines_model` does (does it fit the splines? Just hold create an
object? Create basis functions?)**.

@@

**FIXME add in equations, like from the EPICON paper, to describe them mathematically**

**EAP: Do we need this call to limma by the user, or can these not be done
internally by the `timecourse_differential_expression_analysis` function? We
can still preserve the option of user defining their own, but would be nicer
to make this simpler for the user (e.g. an if clause that tests whether input
is matrix or character vector)**

@@

contrasts = makeContrasts(
	contrasts=timecourse_contrasts,
	levels=levels(meta$Group))

# The function takes the data (data.frame or named matrix), the meta data
# (data.frame containing a timepoint and group column, the first corresponding
# to the time-course information, the latter corresponding to the
# treatment).
pvalues = DE_timecourse(
    data, splines_model, contrasts,
    use_voom_weights=FALSE)
qvalues = apply(pvalues, 2, p.adjust)

@@

```{r}
log_fold_change_timepoints = estimate_log_fold_change(
    data, splines_model, contrasts,  method="timely")
```

@@

```{r}
log_fold_change_epicon = estimate_log_fold_change(
    data, splines_model, contrasts,  method="epicon")

log_fold_change_sum = estimate_log_fold_change(
    data, splines_model, contrasts,  method="sum")

log_fold_change_max = estimate_log_fold_change(
    data, splines_model, contrasts, method="max")

log_fold_change_min = estimate_log_fold_change(
    data, splines_model, contrasts, method="min")
```

>>>>

- Make clear that it applies to RNASeq and how to call the different functions
    to RNASeq
- Check that clustering can deal with count data.

```{r eval=FALSE}
library(devtools)
install_github("NelleV/moanin")

@@

We start by creating the `splines_model` object using the
`create_splines_model` function.

The `splines_model` object contains a number of metadata and options used
throughout this analysis: the condition and timepoints of each samples, the
formula object used or the basis or the degrees of freedom of the model. The
metadata data.frame object should contain at least two columns: one named
`Group`, containing the  treatement effect, and a second one named `Timepoint`
containing the timepoint information.

@@

If no formula is provided, it will default to the following: 
`formula = ~Group:ns(Timepoint, df=degrees_of_fredoom) + Group + 0`.

@@

@@

# The function takes the data (data.frame or named matrix), the meta data
# (data.frame containing a timepoint and group column, the first corresponding
# to the time-course information, the latter corresponding to the
# treatment).
pvalues = DE_timecourse(
    data, splines_model, timecourse_contrasts,
    use_voom_weights=FALSE)
qvalues = apply(pvalues, 2, p.adjust)

@@

```{r}
log_fold_change_timepoints = estimate_log_fold_change(
    data, splines_model, timecourse_contrasts,  method="timely")
```

@@

```{r}
log_fold_change_epicon = estimate_log_fold_change(
    data, splines_model, timecourse_contrasts,  method="epicon")

log_fold_change_sum = estimate_log_fold_change(
    data, splines_model, timecourse_contrasts,  method="sum")

log_fold_change_max = estimate_log_fold_change(
    data, splines_model, timecourse_contrasts, method="max")

log_fold_change_min = estimate_log_fold_change(
    data, splines_model, timecourse_contrasts, method="min")
```
